---
title: '[Practical Machine Learning] Project'
author: "艳儿"
date: "April 9, 2017"
output: html_document
---


## Download Datasets from Websites

To make prediction, we need firstly 
download the training and testing data sets from website.
```{r warning=FALSE, message=FALSE}
library(dplyr)
library(randomForest)
library(caret)

# download data sets
setwd('/Users/Yanfang/Documents/Coursera/Notes/Data Science/Practical Machine Learning')
if(!file.exists('data')) dir.create('data')
trUrl <- 'https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv'
teUrl <- 'https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv'
download.file(trUrl, destfile = './data/pml_training.csv')
download.file(teUrl, destfile = './data/pml_testing.csv')
```

## Read Data into R

After downloading data sets from website, we should load data sets into R.
```{r warning=FALSE, message=FALSE}
# read data into R
trData <- read.csv('./data/pml_training.csv', stringsAsFactors = FALSE, na.strings = c('', 'NA'))
teData <- read.csv('./data/pml_testing.csv', stringsAsFactors =  FALSE, na.strings = c('', 'NA'))

# Explore data analysis
dim(trData)
dim(teData)
colnameTr <- colnames(trData)
colnameTe <- colnames(teData)
```

## Delete Missing Observations and Remove None Relevant Variables

Some features are not useful for prediciton and there exist many missing values in 
data sets, so now we need do some feature enginering. 

```{r warning=FALSE, message=FALSE}
# check if colnames of training data and testing data match
all(colnameTe[-c(1,2,160)] == colnameTe[-c(1, 2, 160)])
# check if there exist NAs 
#apply(trData, 2, function(x) sum(is.na(x)))
colNa <- which(apply(trData, 2, function(x)sum(is.na(x))) >= 19216)
colNa0 <- which(apply(trData, 2, function(x)sum(is.na(x))) > 0)
length(colNa) == length(colNa0)

# delete colname x,user_name and all colNa columns
trData <- trData %>% select(-X, -user_name, -raw_timestamp_part_1, -raw_timestamp_part_2, 
                            -new_window, -num_window, -cvtd_timestamp, -colNa)
teData <- teData %>% select(-X, -user_name, -raw_timestamp_part_1, -raw_timestamp_part_2, 
                            -new_window, -num_window, -cvtd_timestamp, -colNa)
dim(trData)
dim(teData)
```
## Build Random Forest Model and Make Prediction
```{r message=FALSE, warning = FALSE}
# build random forest model
trData$classe <- as.factor(trData$classe)
trainInx <- createDataPartition(trData$classe, p = 0.8, list = FALSE)
trainData <- trData[trainInx, ]
testData <- trData[-trainInx, ] 
dim(trainData)
dim(testData)

rfObj <- randomForest(classe ~., data = trainData, importance = TRUE, ntree = 100)
predY <- predict(rfObj, testData[,-53])
sum(predY == testData$classe)/length(testData$classe)
table(predY, testData$classe)
predtestY <- predict(rfObj, teData[,-53])
predtestY
```

